Grounding the interaction: anchoring situated discourse in everyday human-robot interaction

### 2011-07-15 cover_letter.tex
Addressed comment about multi-lingual support

Typography has been throughly revised for better consistency. Notation varients have been
made explicit (for instance, section 2.4).

\subsection{``p.6, II.E. explain "multi-lingual support"''}

>>>>

Typography has been throughly revised for better consistency. Notation variants have been
made explicit (for instance, section 2.4).

\subsection{``p.6, II.E. Explain "multi-lingual support"''}

The "multi-lingual support" has been reworded:

``fast concept lookup, with possible multi-lingual support (through the
{\tt @lang} XML annotation, labels of concept can be translated, and
specific translations can be queried for)''
